---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qfmtchk

<!-- badges: start -->
<!-- badges: end -->

The goal of qfmtchk is to provide functionalities related to checks and verification of input data for the genetic evaluations at Qualitas AG.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fbzwsqualitasag/qfmtchk")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(qfmtchk)
## basic example code
s_sql_prg_path <- system.file("extdata", "zws_gal_pgb.sql", package = "qfmtchk")
tbl_gal_fmt <- extract_gal_fmt(ps_sql_prg_path = s_sql_prg_path)
```

The above produces a tibble with all column names and the width of the columns.

```{r, echo=FALSE, results='asis'}
cat(rmdhelp::get_latest_change(), "\n")
```

