---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qfmtchk

<!-- badges: start -->
<!-- badges: end -->

The website of `qfmtchk` is available at:  https://fbzwsqualitasag.github.io/qfmtchk/

The goal of qfmtchk is to provide functionalities related to checks and verification of input data for the genetic evaluations at Qualitas AG.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fbzwsqualitasag/qfmtchk")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE, message=FALSE}
library(qfmtchk)
## basic example code
s_sql_prg_path <- system.file("extdata", "zws_gal_pgb.sql", package = "qfmtchk")
tbl_gal_fmt <- extract_gal_fmt(ps_sql_prg_path = s_sql_prg_path)
```

The above produces a tibble with all column names and the width of the columns. This tibble can be improved and corrected at the users convenience with the following command

```{r}
tbl_gal_fmt <- improve_fmt(ptbl_fmt = tbl_gal_fmt,
                           pvec_del_row_idx = 4:6,
                           ptbl_col_rename = tibble::tibble(RowIndex = c(3,6,9),
                                                            NewName=c("BlutanteilAnimal", 
                                                                      "BlutanteilVater", 
                                                                      "Traechtigkeitsdauer")))
```

The improved fmt-tibble can be written to an fmt-file using

```{r}
s_gal_fmt_file <- "gal_check.fmt"
output_fmt(ps_fmt_outfile = s_gal_fmt_file, ptbl_fmt = tbl_gal_fmt)
```

```{r echo=FALSE}
unlink(s_gal_fmt_file)
```



```{r, echo=FALSE, results='asis'}
cat(rmdhelp::get_latest_change(), "\n")
```

