---
title: "Extract Format Information From Export Program"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extract Format Information From Export Program}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(qfmtchk)
library(dplyr)
```


# Disclaimer
Tests and experiments in coming up with format files are described.


# SQL Program
The SQL export program can be used as one possible source of information. The following call produces a first table of columns and positions. The SQL program can be read internally using the following statement.

```{r, message=FALSE, warning=FALSE}
s_sql_export_prg <- system.file("extdata", "zws_gal_pgb.sql", package = "qfmtchk")
s_sql_routine <- "ExportGAL"
s_exp_pattern <- "PA_EXP.sFormat"
vec_prg <- qfmtchk:::read_sql_prg(ps_sql_prg_path    = s_sql_export_prg,
                                  ps_sql_exp_routine = s_sql_routine,
                                  ps_exp_pattern     = s_exp_pattern)
head(vec_prg)
```


The function `extract_gal_fmt()` can be used to directly extract the format information.


```{r, warning=FALSE, message=FALSE}
tbl_gal_fmt <- extract_gal_fmt(ps_sql_prg_path = s_sql_export_prg)
tbl_gal_fmt
```


# Improvements
Based on the code some manual improvements have to be made. The following list shows all improvements. 

1. Row 3 contains the blood content of the animal

```{r, eval=FALSE}
tbl_gal_fmt$ColName[3] <- "BlutanteilAnimal"
```

2. Rows 4-6 are a duplicate of rows 7-9

```{r, eval=FALSE}
tbl_gal_fmt <- tbl_gal_fmt %>% slice(-(4:6))
```

3. Row 6 corresponds to the blood content of the sire

```{r, eval=FALSE}
tbl_gal_fmt$ColName[6] <- "BlutanteilVater"
```

4. Row 9 corresponds to duration of pregancy

```{r, eval=FALSE}
tbl_gal_fmt$ColName[9] <- "Traechtigkeitsdauer"
```

The above steps can also be done with the following function call

```{r}
tbl_gal_fmt <- improve_fmt(ptbl_fmt = tbl_gal_fmt,
                           pvec_del_row_idx = 4:6,
                           ptbl_col_rename = tibble::tibble(RowIndex = c(3,6,9),
                                                            NewName=c("BlutanteilAnimal", 
                                                                      "BlutanteilVater", 
                                                                      "Traechtigkeitsdauer")))

```


# Check

```{r}
knitr::kable(tbl_gal_fmt)
```



# Output
Write an output-fmt file.

```{r}
s_gal_fmt_file <- "gal_check.fmt"
if (file.exists(s_gal_fmt_file)) unlink(s_gal_fmt_file)
n_nr_fmt_rec <- nrow(tbl_gal_fmt)
# start with first line outside of loop
for (idx in 1:n_nr_fmt_rec){
  cat("# ", tbl_gal_fmt$ColName[idx], "\n", sep = "", file = s_gal_fmt_file, append = TRUE)
  cat("[", tbl_gal_fmt$StartPos[idx], "-", tbl_gal_fmt$EndPos[idx], "]\n", sep = "", file = s_gal_fmt_file, append = TRUE)
  cat("data_required=True \n\n", sep = "", file = s_gal_fmt_file, append = TRUE)
}
```

The same output can be produced by the following function call.

```{r}
output_fmt(ps_fmt_outfile = s_gal_fmt_file, ptbl_fmt = tbl_gal_fmt)
```

The first few lines of the produced file is

```{r}
cat(head(readLines(s_gal_fmt_file), n=10L), sep = "\n")
```


```{r, echo=FALSE, results='asis'}
cat(rmdhelp::get_latest_change(), "\n")
```
