---
title: "Format Information For Carcass Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Format Information For Carcass Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qfmtchk)
```

# Disclaimer
This vignette shows how to extract data formats from the import routine of the carcass data (KLDAT) obtained from the Identitas database (TVD).


# Reading SQL Program
In a first step, the SQL statements from the import routine are read. This is done internally in the extraction function. For reasons of checking, the import routine is read with the following statement

```{r, message=FALSE, warning=FALSE}
s_sql_prg <- system.file("extdata", "dsch_imp_3_pgb.sql", package = "qfmtchk")
s_sql_routine <- "ImportSchlachtdatenTvd"
s_exp_pattern <- "rowSTV.STV"
vec_prg <- qfmtchk:::read_sql_prg(ps_sql_prg_path    = s_sql_prg,
                                  ps_sql_exp_routine = s_sql_routine,
                                  ps_exp_pattern     = s_exp_pattern)
head(vec_prg)
```


# Format Extraction
The format information can be extracted into a tibble with 

```{r, message=FALSE, warning=FALSE}
tbl_kldat_fmt <- extract_kldat_fmt(ps_sql_prg_path = s_sql_prg)
knitr::kable(tbl_kldat_fmt)
```


# Output
As it seams with the above extracted format information, improvements are not required. Hence, we can directly write the fmt information to a file.

```{r}
s_kldat_fmt_file <- "kldat_check.fmt"
output_fmt(ps_fmt_outfile = s_kldat_fmt_file, ptbl_fmt = tbl_kldat_fmt)
```

The following chunk is checking the content of the created file

```{r}
cat(head(readLines(s_kldat_fmt_file), n=10L), sep = "\n")
```


```{r, echo=FALSE, results='asis'}
cat(rmdhelp::get_latest_change(), "\n")
```
